---
title: DV_RProject1
author: Brian Yeh, Valentina Chen
output: html_document
---

###Load Required packages
```{r echo=FALSE, message=FALSE}
require("jsonlite")
require("RCurl")
require(extrafont)
require("ggplot2")

```

###Summary of dataframe  
SQL Query: select * from titanic
```{r}

df <- data.frame(fromJSON(getURL(URLencode('129.152.144.84:5001/rest/native/?query="select * from titanic"'),httpheader=c(DB='jdbc:oracle:thin:@129.152.144.84:1521/PDBF15DV.usuniversi01134.oraclecloud.internal', USER='cs329e_by2578', PASS='orcl_by2578', MODE='native_mode', MODEL='model', returnDimensions = 'False', returnFor = 'JSON'), verbose = TRUE), ))

summary(df)
```

###Subset of dataframe: Males over the age of 40 who survived
```{r}
df.sub <- subset(df, SURVIVED == 1 & SEX == "male" & as.numeric(AGE) > 40)
df.sub
```

```{r warning=FALSE}

ggplot() + 
  coord_cartesian() + 
  scale_x_continuous() +
  scale_y_continuous() +
  #facet_grid(PCLASS~SURVIVED) +
  labs(title='Titanic') +
  labs(x="Age", y=paste("Fare")) +
  layer(data=df, 
        mapping=aes(x=as.numeric(as.character(AGE)), y=as.numeric(as.character(FARE)), color=SEX), 
        stat="identity", 
        stat_params=list(), 
        geom="point",
        geom_params=list(), 
        #position=position_identity()
        position=position_jitter(width=0.3, height=0)
  )
```

SQL Query: select * from titanic where sex is not null

```{r}

df <- data.frame(fromJSON(getURL(URLencode('129.152.144.84:5001/rest/native/?query="select * from titanic where sex is not null"'),httpheader=c(DB='jdbc:oracle:thin:@129.152.144.84:1521/PDBF15DV.usuniversi01134.oraclecloud.internal', USER='cs329e_by2578', PASS='orcl_by2578', MODE='native_mode', MODEL='model', returnDimensions = 'False', returnFor = 'JSON'), verbose = TRUE), ))

ggplot() + 
  coord_cartesian() + 
  scale_x_continuous() +
  scale_y_continuous() +
  #facet_grid(PCLASS~SURVIVED) +
  labs(title='Titanic') +
  labs(x="Age", y=paste("Fare")) +
  layer(data=df, 
        mapping=aes(x=as.numeric(as.character(AGE)), y=as.numeric(as.character(FARE)), color=SEX), 
        stat="identity", 
        stat_params=list(), 
        geom="point",
        geom_params=list(), 
        #position=position_identity()
        position=position_jitter(width=0.3, height=0)
  )
```

```{r warning=FALSE}

ggplot() + 
  coord_cartesian() + 
  scale_x_discrete() +
  scale_y_continuous() +
  #facet_grid(PCLASS~SURVIVED) +
  labs(title='Titanic') +
  labs(x="Survived", y=paste("Fare")) +
  layer(data=df, 
        mapping=aes(x=SEX, y=as.numeric(as.character(FARE)), color=as.character(SURVIVED)), 
        stat="identity", 
        stat_params=list(), 
        geom="point",
        geom_params=list(), 
        #position=position_identity()
        position=position_jitter(width=0.3, height=0)
  )


ggplot() + 
  coord_cartesian() + 
  scale_x_discrete() +
  scale_y_continuous() +
  facet_grid(PCLASS~SURVIVED, labeller=label_both) +
  labs(title='Titanic') +
  labs(x="SURVIVED", y=paste("FARE")) +
  layer(data=df, 
        mapping=aes(x=SEX, y=as.numeric(as.character(FARE)), color=SEX), 
        stat="identity", 
        stat_params=list(), 
        geom="point",
        geom_params=list(), 
        #position=position_identity()
        position=position_jitter(width=0.3, height=0)
  )

```

SQL Query = select * from titanic where age <= 10
```{r warning=FALSE}
df <- data.frame(fromJSON(getURL(URLencode('129.152.144.84:5001/rest/native/?query="select * from titanic where age <= 10"'),httpheader=c(DB='jdbc:oracle:thin:@129.152.144.84:1521/PDBF15DV.usuniversi01134.oraclecloud.internal', USER='cs329e_by2578', PASS='orcl_by2578', MODE='native_mode', MODEL='model', returnDimensions = 'False', returnFor = 'JSON'), verbose = TRUE), ))


ggplot() + 
  coord_cartesian() + 
  scale_x_discrete() +
  scale_y_continuous() +
  facet_grid(PCLASS~SURVIVED, labeller=label_both) +
  labs(title='Titanic where age <=10') +
  labs(x="SURVIVED", y=paste("FARE")) +
  layer(data=df, 
        mapping=aes(x=SEX, y=as.numeric(as.character(FARE)), color=SEX), 
        stat="identity", 
        stat_params=list(), 
        geom="point",
        geom_params=list(), 
        #position=position_identity()
        position=position_jitter(width=0.3, height=0)
  )

```
  
###Visualization of the number of people who survived based on age and sex
Interesting to see how more females survived overrall. However, many of the young men also survived at similar rates to females.  
SQL Query = select * from titanic where AGE is not null
```{r}
df <- data.frame(fromJSON(getURL(URLencode('129.152.144.84:5001/rest/native/?query="select * from titanic where AGE is not null"'),httpheader=c(DB='jdbc:oracle:thin:@129.152.144.84:1521/PDBF15DV.usuniversi01134.oraclecloud.internal', USER='cs329e_by2578', PASS='orcl_by2578', MODE='native_mode', MODEL='model', returnDimensions = 'False', returnFor = 'JSON'), verbose = TRUE), ))

ggplot() + 
  coord_cartesian() + 
  scale_x_discrete() +
  scale_y_continuous() +
  #facet_grid(PCLASS~SURVIVED) +
  labs(title='Titanic') +
  labs(x="Survived", y=paste("AGE")) +
  layer(data=df, 
        mapping=aes(x=SEX, y=as.numeric(AGE), color=as.character(SURVIVED)), 
#         stat="identity", 
#         stat_params=list(), 
         geom="point",
         geom_params=list(), 
        #position=position_identity()
        position=position_jitter(width=0.3, height=0)
  )
```
